% !TEX TS-program = lualatex

\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{lmodern}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{xcolor}

\usepackage{datenumber}
\usepackage{calc}

\newcounter{datetoday}
\newcounter{diffyears}
\newcounter{diffmonths}
\newcounter{diffdays}

% based on the 
% https://tex.stackexchange.com/a/14519/204629
\newcommand{\difftoday}[3]{%
      \setmydatenumber{datetoday}{\the\year}{\the\month}{\the\day}%
      \setmydatenumber{diffdays}{#1}{#2}{#3}%
      \addtocounter{diffdays}{-\thedatetoday}%
      \ifnum\value{diffdays}>0
        \def\diffbefore{in }%
      \else
        \def\diffbefore{}%
        \setcounter{diffdays}{-\value{diffdays}}%
      \fi
      \setcounter{diffyears}{\value{diffdays}/365}%
      \setcounter{diffdays}{\value{diffdays}-365*\value{diffyears}}%
      \setcounter{diffmonths}{\value{diffdays}/30}%
      \setcounter{diffdays}{\value{diffdays}-30*\value{diffmonths}}%
      %
      \diffbefore
      \ifnum\value{diffyears}=0
      \else
        \ifnum\value{diffyears}>1
            \thediffyears\space years
        \else
            \thediffyears\space year
        \fi
      \fi
}
 
\pagestyle{fancy}
\fancyhf{}
\lfoot{\small References are available on request}
\rfoot{\small \the\year\hspace{6pt}Artem Chepurnoy}
\renewcommand{\headrulewidth}{0pt}

\input{public}
%\input{private}

\begin{document}
	\begin{center}
		{\huge\bfseries Android Developer} \\[1em]
		{\Large Artem Chepurnoy} \\[1em]
		\faMapMarker \quad \myaddress
	\end{center}
	\vspace{1em}
	\textit{\faPaperPlane \quad mail@artemchep.com} \hspace*{\fill} \textit{\faPhone \quad \myphone} 

	\section*{Personal Statement}
	A versatile and professional software developer with a commitment to and experience of developing innovative and complex software solutions. 
	More than \difftoday{2011}{08}{19} of experience in developing software.

	\section*{Skills}
	\subsection*{General}
	\begin{multicols}{2}
	\begin{itemize}
		\item \textbf{Programming} with Kotlin, Java, JavaScript, Dart, Python etc.
		\item \textbf{Native Android apps} with Kotlin, Java, \textbf{multiplatform apps} with Kotlin \& Compose \textbf{crossplatform apps} with Dart \& Flutter, JavaScript.
		\item \textbf{Building} with Gradle, Webpack, Maven, \textbf{CI/CD} with GitHub actions, GitLab CI, Fastlane etc.
		\item \textbf{Designing apps} with Object-Oriented and Functional programming principles, Hexagonal and Clean architecture, MVVM, MVI, MVP patterns and more.
		\item \textbf{Databases} with SQL, NoSQL.
		\item \textbf{Backend} with ktor, NodeJS.
		\item \textbf{Version control} with Git.
		\item \textbf{English} with upper intermediate (B2) level.
	\end{itemize}
	\end{multicols}
	\subsection*{Android}
	\begin{multicols}{2}
	\begin{itemize}
		\item \textbf{Advanced at} Kotlin, Reactive programming, Architecture design.
		\item \textbf{Strong at} Compose, Custom Views, Background/Foreground Services, Navigation, JetPack, Multithreading, Memory management, Security, Gradle, Phone \& Tablet support, CI, DI, etc.
		\item \textbf{Good at} Video streaming, Databases, Bluetooth, Wear OS, OpenGL ES, etc.
	\end{itemize}
	\end{multicols}
	
	{ \footnotesize
	A few libraries I often use: androidx.*, kotlinx.*, arrow-kt, kodein-di, okhttp, retrofit, moshi, room, glide \& coil, exo-player.       
	}
	
	\section*{Experience}
	\begin{tabular}{@{}l@{\enspace--\enspace}ll}
		\textbf{2020 Aug.} & Present & Tech Lead of Android Department at \href{https://chisw.com}{\textbf{CHI Software}}. \\
	\end{tabular} \\[0.2em]
	Interviewing Android \& Flutter developers, Managing the Department \& Developers development plans, Maintaining internal projects, Technical \& Performance reviews, Code reviews, Tech-talks, Estimating projects, Mentoring and App development. \\[0.4em]
	\begin{tabular}{@{}l@{\enspace--\enspace}ll}
		\textbf{2018 Feb.} & \textbf{2020 Aug.} & Android App Developer at \href{https://chisw.com}{\textbf{CHI Software}}. \\
	\end{tabular} \\[0.2em]
	Interviewing Android \& Flutter developers, Estimating projects, Mentoring and App development.  \\[0.4em]   
	\begin{tabular}{@{}l@{\enspace--\enspace}ll}
		\textbf{2015 Mar.} & \textbf{2017 Aug.} & Android App Developer at \textbf{Corgi Inc}. \\
	\end{tabular} \\[0.2em]
	App development, User interface \& User experience design.   \\[0.4em]   
	\begin{tabular}{@{}l@{\enspace--\enspace}ll}
		\textbf{2012 Jan.} & Present & Self-employed \\
	\end{tabular} \\[0.2em]
	Development from scratch, some of the projects are listed on my GitHub and Play Store accounts (see links in profiles section).   

	\section*{Projects}
	\subsection*{Personal projects}
	Some of my personal projects are listed below. Most of these projects are \textbf{open source}, titles are clickable.
	\begin{itemize}
		\item \faAndroid \enskip \href{http://artemchep.com/acdisplay/}{\textbf{AcDisplay}} --- The predecesor of Android's always on display. \\[0.2em]
		{\footnotesize \{Java, Python, IAP\} \hfill [2013--2015]} \\[0.2em]
		\textit{AcDisplay has been installed over a three million times on Google Play.} 

		\item \faAndroid \enskip \faLinux \enskip \href{https://github.com/AChep/keyguard-app}{\textbf{Keyguard}} --- Multifplatform Bitwarden client. \\[0.2em]
		{\footnotesize \{Koltin, Kotlin multiplatform, Coroutines, JetPack Compose, Crypto, SQL \& more \} \hfill [2021--Present]} \\[0.2em]
		Key features: encrypted state, fluent animations, multiplatform support, multiaccount support, watchtower. 

		\item \faAndroid \enskip \faChrome \enskip \faLinux \enskip \href{https://github.com/AChep/15puzzle}{\textbf{Game of Fifteen}} --- Best fifteen puzzle. \\[0.2em]
		{\footnotesize \{Dart, Flutter, IAP, Flutter $\Leftrightarrow$ Android, encrypt\} \hfill [2018--Present]} \\[0.2em]
		Key features: natural controls and animations, encrypted state, consistently highc complexity level of generated puzzles, dark and light theme, tablet/web/linux support. 
		
		\item \faAndroid \enskip \href{https://github.com/AChep/PocketMode}{\textbf{Pocket mode}} --- Lock your phone by hovering the proximity sensor. \\[0.2em]
		{\footnotesize \{Kotlin, Coroutines, MVVM, IAP, RenderScript\} \hfill [2018--Present]} \\[0.2em]
		Key features: modularity, customizability, dark theme support, turns screen off without requiring the pin on next unlock.   
		
		\item \faAndroid \enskip \href{https://github.com/AChep/literaryclock}{\textbf{Literary Clock}} --- Time in a form of literature quotes. \\[0.2em]
		{\footnotesize \{Kotlin, Coroutines, Firebase, MVVM, Realm\} \hfill [2018--Present]} \\[0.2em]
		Key features: syncronization with a Firebase server, local cache, widget, screen saver.  
			
		\item \faAndroid \enskip \href{https://github.com/AChep/horlogo}{\textbf{Horlogo}} --- Exemplary stylish simple watch face. \\[0.2em]
		{\footnotesize \{Kotlin, Coroutines, MVP, IAP\} \hfill [2018--Present]} \\[0.2em]
		Key features: modularity, sync between Wear OS and corresponding Android app, use of View's rending under the hood.   
			
		\item \faAndroid \enskip \href{https://github.com/AChep/materialwatch}{\textbf{Material Watch}} --- Watch face inspired by the Material You design system. \\[0.2em]
		{\footnotesize \{Kotlin, Coroutines, MVVM\} \hfill [2021--Present]} \\[0.2em]
		Key features: modularity, excessive use of \texttt{Flow}, sync between Wear OS and corresponding Android app, transition animations.   
		
		\item \faAndroid \enskip \href{https://github.com/AChep/essence}{\textbf{Essence}} --- Circular powerful watch face. \\[0.2em]
		{\footnotesize \{Kotlin, Coroutines, MVVM, RenderScript\} \hfill [2019--Present]} \\[0.2em]
		Key features: modularity, excessive use of \texttt{Flow}, circular RenderScript shader, sync between Wear OS and corresponding Android app, use of View's rending under the hood.  
		
		\item {\footnotesize \faAndroid \enskip \href{https://github.com/AChep/acpods}{\textbf{AcPods}} [2018--Present] --- Helps with intergation of Apple's AirPods. Designed and implemented the concept. Key features: modularity, hexagonal architecture, decoding of AirPods state.}   
		
		\item {\footnotesize \faAndroid \enskip \href{http://artemchep.com/horario/}{\textbf{Horario}} [2016--2018] --- Learning muliplatform platform for students that aims to improving communication between students and teachers. Designed and implemented the concept, designed the model of document-oriented database for platform, designed the logo, designed and implemented architecture to support both phones and tablets, maintainer of repository.} 
		
		\item {\footnotesize \faAndroid \enskip \href{https://forum.xda-developers.com/showthread.php?t=1188486}{\textbf{GingerDX}} [2012--2013] --- Fast, smooth and lightweight CyanogenMOD 7 based ROM with some special features. Added motion gestures to the alarm app (merged into LineageOS later on), modified system UI to be looking like Android 4.x.}
		
		\item {\footnotesize \href{https://github.com/AChep/SudokuSolver}{\textbf{SudokuSolver}} [2015--2015] --- Simple sudoku-solver that can be used to solve or help to generate sudokus.}
	\end{itemize}
	
	\subsection*{Company projects}
	\begin{itemize}
		\item \faAndroid \faLinux \enskip Multi-client app for playing videos \& games. \\[0.2em]
		{\footnotesize Android Developer, used \{Kotlin, Kotlin multiplatform, Coroutines, Arrow, MVVM, Kodein, clean, moshi, Unity, NanoHTTPD, ExoPlayer, glide, adobe experience, IAP, datastore \& more \} \hfill [2020--Present]} \\[0.2em]
		Development from scratch. Maintained and leaded the Android / CI / Desktop projects. Key features: more than 80 modules, custom navigation handling, using ExoPlayer's cache to cache all content, custom views, screens \& nav graph are defined by the .json, Unity games, Web games with ktor, per-client features, shared modules between Android \& iOS \& Deskop, CI/CD, exstensive use of reactive patterns and many many more. 
  
		\item \faAndroid \enskip Social network for Truck drivers. \\[0.2em]
		{\footnotesize Architect, used \{AWS, Kotlin, Compose, Swift\} \hfill [2023--2023]} \\[0.2em]
		Designed the high level architecture of a project, leaded the development of both backend and mobile teams, code reviews.
		
		\item \faAndroid \enskip Restaurant reservation platform. \\[0.2em]
		{\footnotesize Android Developer, used \{Kotlin, Coroutines, MVVM, Dagger, clean, data binding \& more \} \hfill [2020--2021]} \\[0.2em]
		Maintained the project, leaded its refactoring. Redesigned parts of the app, developed new features.
		
		\item \faAndroid \enskip \href{http://getcorgi.com/}{\textbf{Corgi for Feedly}} --- Your feed right on the lock screen. \\[0.2em]
		{\footnotesize Software Engineer \& Designer at Corgi Inc., used \{Java, Retrofit, RX, Butterknife, Glide, OkHttp, GSON\} \hfill [2015--2017]} \\[0.2em]
		Designed and developed the Android Keyguard and Notifications modules, implemented the graphical user interface, helped to design the concept of \textit{extended} lock screen, helped to maintain git-repository of the project.
		
		\item \faAndroid \enskip Lets you connect with people and easily exchange benefits. \\[0.2em]
		{\footnotesize Android Developer, used \{Kotlin, Coroutines, Firebase, dirty MVVM, Kodein, dirty clean, Jackson, Nitrite\} \hfill [2018--2019]} \\[0.2em]
		Maintained the project, dragastically improved the performance of the app, migrated from Kotlin 1.2 to 1.3, migrated to AndroidX, redesigned parts of the app.
		
		\item \faAndroid \enskip Order \& Pay for the food. \\[0.2em]
		{\footnotesize Android Developer \& Designer, used \{Java, Retrofit, OkHttp, Glide, GSON\} \hfill [2018-2018]} \\[0.2em]
		Developed a module for ordering food from the restaurants, suggested the changes in the app's design which were implemented later on. 
		
		\item \faAndroid \enskip Sports client management. \\[0.2em]
		{\footnotesize Android Developer, used \{Kotlin, Coroutines, Firebase, MVP, Glide\} \hfill [2018--2018]} \\[0.2em]
		Leaded the development of the app, helped to fix the existing issues with Firebase database, helped to fix the exisiting issues of the web-client written on Angular, maintaned the CI/CD server.

	\end{itemize}
	and many more that are not finished/still in development/not fun enough.
	
	\subsection*{Profiles}
	\begin{tabular}{@{}lll}
		\faGithub & GitHub & \href{https://github.com/AChep}{\texttt{github.com/AChep}} \\
		\faLinkedin & LinkedIn & \href{https://www.linkedin.com/in/artemchep/}{\texttt{linkedin.com/in/artemchep}} \\
		\faStackOverflow & Stack Overflow & \href{https://stackoverflow.com/users/1408535/achep}{\texttt{stackoverflow.com/users/1408535/achep}} \\
		\faPlay & Play Store & \href{https://play.google.com/store/apps/dev?id=8988387544477629485}{\texttt{play.google.com/store/apps/dev?id=8988387544477629485}} \\
	\end{tabular}
	
	\subsection*{Publications}
	\begin{itemize}
		\item \textbf{Android Coroutine. Guide for beginners} (\textit{Russian lang.}), published on \href{https://dou.ua/forums/topic/33173/}{\texttt{dou.ua}} with a mirror available on \href{https://docs.google.com/document/d/1PtQ5UjAo0gpSBVRP7VUO1cWeLKR4_pi1KOihPlNiB18}{\texttt{Google Docs}}
	\end{itemize}

	\section*{Education}
	\textbf{2014 -- 2018 (bachelor's degree), 2018 -- 2020 (master's degree), National Technical University <<Kharkiv polytechnic institute>> Software Engineering and Management Information Technologies}. \\
	Modules included Machine learning, Fuzzy technologies, Calculus, Database modeling, Software testing, Software analysis and modeling, Requirements analysis etc.
	
	\section*{Certificates}
	\subsection*{Cambridge Certification Authority}
	\begin{itemize}
		\item \textbf{Java Level 1}, completed on 1st March 2018
		\item \textbf{Python Level 1}, completed on 1st March 2018
	\end{itemize}

	\section*{Achievements}
	Recognized Developer on \href{https://forum.xda-developers.com/member.php?u=3685328}{XDA-Developers} from 2013 to present time, Recognized Themer from 2013 to 2018.
	A prizewinner of multiple regional olympiads in Programming, Information Technology, Astronomy and Math.

\end{document}
